Statically Typed String Sanitation Inside a Python (Technical Report)

### 2014-11-21 sanitation-psp14/tr/strings_chapter.tex
PSP14TR - fixed formating

\documentclass[12pt]{article}

\usepackage{lineno}

\usepackage{afterpage}
\usepackage{listings}
\usepackage[usenames,dvipsnames]{color}
\usepackage{mathpartir}
\usepackage{amsmath}
\usepackage{amssymb}

% Hack. Something's wrong with PLAS paper when using the ACM Proc docclass
\let\proof\relax
\let\endproof\relax
\usepackage{amsthm}

\usepackage[nomarkers,figuresonly]{endfloat}
\renewcommand{\efloatseparator}{\vfill}

\usepackage{ stmaryrd }
\usepackage{verbatimbox}
\input{../../att-icfp14/macros-atlam}
\usepackage{alltt}
\renewcommand{\ttdefault}{txtt}
\usepackage{color}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\definecolor{light-gray}{gray}{0.5}
\usepackage{listings}
\usepackage{wasysym}
    \makeatletter
\usepackage{enumitem}
\usepackage{enumerate}

% \btIfInRange{number}{range list}{TRUE}{FALSE}
%
% Test if int number <number> is element of a (comma separated) list of ranges
% (such as: {1,3-5,7,10-12,14}) and processes <TRUE> or <FALSE> respectively
%
        \newcount\bt@rangea
        \newcount\bt@rangeb

        \newcommand\btIfInRange[2]{%
            \global\let\bt@inrange\@secondoftwo%
            \edef\bt@rangelist{#2}%
            \foreach \range in \bt@rangelist {%
                \afterassignment\bt@getrangeb%
                \bt@rangea=0\range\relax%
                \pgfmathtruncatemacro\result{ ( #1 >= \bt@rangea) && (#1 <= \bt@rangeb) }%
                \ifnum\result=1\relax%
                    \breakforeach%
                    \global\let\bt@inrange\@firstoftwo%
                \fi%
            }%
            \bt@inrange%
        }

        \newcommand\bt@getrangeb{%
            \@ifnextchar\relax%
            {\bt@rangeb=\bt@rangea}%
            {\@getrangeb}%
        }

        \def\@getrangeb-#1\relax{%
            \ifx\relax#1\relax%
                \bt@rangeb=100000%   \maxdimen is too large for pgfmath
            \else%
                \bt@rangeb=#1\relax%
            \fi%
        }

%
% \btLstHL{range list}
%
        \newcommand{\btLstHL}[1]{%
            \btIfInRange{\value{lstnumber}}{#1}%
            {\color{black!10}}%
            {\def\lst@linebgrd}%
        }%

%
% \btInputEmph[listing options]{range list}{file name}
%
        \newcommand{\btLstInputEmph}[3][\empty]{%
            \lstset{%
                linebackgroundcolor=\btLstHL{#2}%
                \lstinputlisting{#3}%
            }% \only
        }

% Patch line number key to call line background macro
        \lst@Key{numbers}{none}{%
            \def\lst@PlaceNumber{\lst@linebgrd}%
            \lstKV@SwitchCases{#1}{%
                none&\\%
                left&\def\lst@PlaceNumber{\llap{\normalfont
                \lst@numberstyle{\thelstnumber}\kern\lst@numbersep}\lst@linebgrd}\\%
                right&\def\lst@PlaceNumber{\rlap{\normalfont
                \kern\linewidth \kern\lst@numbersep
                \lst@numberstyle{\thelstnumber}}\lst@linebgrd}%
            }{%
                \PackageError{Listings}{Numbers #1 unknown}\@ehc%
            }%
        }

% New keys
        \lst@Key{linebackgroundcolor}{}{%
            \def\lst@linebgrdcolor{#1}%
        }
        \lst@Key{linebackgroundsep}{0pt}{%
            \def\lst@linebgrdsep{#1}%
        }
        \lst@Key{linebackgroundwidth}{\linewidth}{%
            \def\lst@linebgrdwidth{#1}%
        }
        \lst@Key{linebackgroundheight}{\ht\strutbox}{%
            \def\lst@linebgrdheight{#1}%
        }
        \lst@Key{linebackgrounddepth}{\dp\strutbox}{%
            \def\lst@linebgrddepth{#1}%
        }
        \lst@Key{linebackgroundcmd}{\color@block}{%
            \def\lst@linebgrdcmd{#1}%
        }

% Line Background macro
        \newcommand{\lst@linebgrd}{%
            \ifx\lst@linebgrdcolor\empty\else
                \rlap{%
                    \lst@basicstyle
                    \color{-.}% By default use the opposite (`-`) of the current color (`.`) as background
                    \lst@linebgrdcolor{%
                        \kern-\dimexpr\lst@linebgrdsep\relax%
                        \lst@linebgrdcmd{\lst@linebgrdwidth}{\lst@linebgrdheight}{\lst@linebgrddepth}%
                    }%
                }%
            \fi
        }

 % Heather-added packages for the fancy table
 \usepackage{longtable}
 \usepackage{booktabs}
 \usepackage{pdflscape}
 \usepackage{colortbl}%
 \newcommand{\myrowcolour}{\rowcolor[gray]{0.925}}
 \usepackage{wasysym}

    \makeatother

\lstset{
  language=Python,
  showstringspaces=false,
  formfeed=\newpage,
  tabsize=4,
  commentstyle=\itshape\color{light-gray},
  basicstyle=\ttfamily\scriptsize,
  morekeywords={lambda, self, assert, as, cls},
  numbers=left,
  numberstyle=\scriptsize\color{light-gray}\textsf,
  xleftmargin=2em,
  stringstyle=\color{mauve}
}
\lstdefinestyle{Bash}{
    language={}, 
    numbers=left,
    numberstyle=\scriptsize\color{light-gray}\textsf,
    moredelim=**[is][\color{blue}\bf\ttfamily]{`}{`},
}
\lstdefinestyle{OpenCL}{
	language=C++,
	morekeywords={kernel, __kernel, global, __global, size_t, get_global_id, sin, printf, int2}
}

\usepackage{float}
\floatstyle{ruled}
\newfloat{codelisting}{tp}{lop}
\floatname{codelisting}{Listing}
\setlength{\floatsep}{10pt}
\setlength{\textfloatsep}{10pt}

\usepackage{url}

%\usepackage{todo}
%\usepackage[subject={Todo},author={Josef}]{pdfcomment}
%\usepackage{cooltooltips}
\newcommand{\todo}[1]{{\color{red} #1}}
\usepackage{placeins}

\usepackage{textpos}

\renewcommand\topfraction{0.85}
\renewcommand\bottomfraction{0.85}
\renewcommand\textfraction{0.1}
\renewcommand\floatpagefraction{0.85}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{bussproofs}    % Gentzen-style deduction trees *with aligned sequents!*
\usepackage{mathpartir}	% For type-settting type checking rule figures
\usepackage{syntax}		% For type-setting formal grammars.

\usepackage{hyperref}		% For links in citations

\usepackage{float}			% Make figures float if [H] option is passed.

\iffalse
\usepackage{listings}		% For typesetting code listings
\usepackage{callout}
\usepackage{titlesec}
\usepackage[T1]{fontenc}
\usepackage{upquote}
\lstset{upquote=true}
\fi

\usepackage{textcomp}		% For \textquotesingle as used in introduction
\usepackage{color}			% for box colors, like in TAPL.

\usepackage{amsmath}		% Begin Carthage default packages
\usepackage{makeidx}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphics}
\usepackage{enumerate}
\usepackage{multicol}
\usepackage{epsfig}
\usepackage{csquotes}
\usepackage{enumitem}

@@

\title{Statically Typed String Sanitation Inside a Python: Technical Report}
\author{Nathan Fulton\and Cyrus Omar\and Jonathan Aldrich}

\begin{document}
\linenumbers

\maketitle

\begin{abstract}
Web applications must ultimately command systems like web browsers and database engines using strings. Strings derived from improperly sanitized user input  can thus be a vector for command injection attacks.

In this report, we introduce \emph{regular string types}, which classify strings known statically to be in a specified regular language. These types come equipped with common operations like concatenation, substitution and coercion, so they  can be used to implement, in a conventional manner, the portions of a web application or application framework that must directly construct command strings. Simple type annotations at key interfaces can be used to statically verify that sanitization has been performed correctly without introducing redundant run-time checks. We specify this type system in a minimal typed lambda calculus, $\lambda_{RS}$.

We then specify a translation from $\lambda_{RS}$ to a language fragment containing only standard strings and regular expressions and prove that the correctness theorem for
$\lambda_{RS}$ is preserved under translation.
\end{abstract}

\section{Introduction}

Command injection vulnerabilities are among the most common and severe security vulnerabilities in modern web applications.  They arise because web applications, at their boundaries, control external systems using commands represented as  strings. In \cite{fulton2014} the authors argue that extensible type systems are an attractive solution to this important security problem. This Technical Report contains supporting evidence for claims put forth and explained in \cite{fulton2014}, including proofs of lemmas
and theorems asserted in the paper, examples, and additional discussion of the paper's technical content.

Theorems and lemmas appearing in \cite{fulton2014} are numbered, while supporting facts appearing only in the Technical Report are lettered.
Numbered items correspond to the numbering in \cite{fulton2014}.

\section{Proofs of Lemmas and Theorems about $\lambdas$}

@@

\bibliographystyle{abbrv}

\bibliography{research}

\end{document}

>>>>

\documentclass[11pt,leqno]{article}
\usepackage{cmu-titlepage2}
\usepackage{fullpage}
\usepackage[small,bf]{caption2}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}

\usepackage{amsmath}
\usepackage{amssymb} 
\usepackage{amsthm}
\usepackage{ stmaryrd }
\usepackage{mathpartir}
\usepackage{enumerate}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{tabularx}
\usepackage{morefloats}
\usepackage{bussproofs}    % Gentzen-style deduction trees *with aligned sequents!*
\usepackage{mathpartir}    % For type-settting type checking rule figures
\usepackage{syntax}        % For type-setting formal grammars.
\usepackage{hyperref}       % For links in citations
\usepackage{enumerate}
\usepackage{enumitem}

\input{../../att-icfp14/macros-atlam}

\usepackage{todonotes}

@@

\title{Statically Typed String Sanitation Inside a Python (Technical Report)}
\author{Nathan Fulton \and Cyrus Omar \and Jonathan Aldrich}
\date{December 2014}
\trnumber{CMU-ISR-14-112}
\keywords{type systems; regular languages; input sanitation; string sanitation}
\support{This work was supported by the National Security Agency lablet contract \#H98230-14-C-0140.}
\abstract{This report contains supporting evidence for claims put forth and explained in the paper ``Statically Typed String Sanitation Inside a Python'' \cite{fulton2014}, including proofs of lemmas
and theorems asserted in the paper, examples, and additional discussion of the paper's technical content.}
\begin{document}
\maketitle
\section{Terminology and Notation}
Theorems and lemmas appearing in \cite{fulton2014} are numbered, while supporting facts appearing only in the Technical Report are lettered.
Numbered items correspond to the numbering in \cite{fulton2014}.

\section{$\lambdas$}

@@

\bibliographystyle{abbrv}
\bibliography{research}
\end{document}
